02\_graphlet\_correlation\_Analysis

### 2018-03-08 notebook.tex
added papers

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{Thresholding\_local}

@@

    \section{Local Thresholding}\label{local-thresholding}

In this notebook, I extract orbits for a signle chromosome in all 4 cell
lines, using a different method of thresholding. In order to do this, I
slide a kernel of size k through each pixel and check if it has a
particular property. If the property is satisified, then the pixel is
set to 1, otherwise it is set to 0. The two properties that I experiment
with are \emph{maximum thresholding} and \emph{normal thresholding}. 1.
\textbf{Maximum Thresholding}: in max thresholding, if the pixel is the
maximum of its neighbors with respect to the kernel, then it is set. 2.
\textbf{Normal Thresholding}: in normal thresholding, if the pixel is
larger that the average of the neighbors then it is set.

first I perform the most lates normalization method that I have found to
be most useful: a combination of gaussian normalization, SCN and pearson
correlation, in the same order mentioned. The normalized results are of
type \texttt{pearson(scn(gaussian(graph)))}.

Then I threshold the results by setting pearson values larger than 0 to
1 and the rest to 0. In order to extract graphlets, I used the
\emph{orca} package in R. the script \texttt{./rscript.r} read a binary
thresholded matrix representing an unweighted graph and outputs orbtis 0
through 72 for each node in the network. After thredholding the
matrices, I save them so that orca in R can read it and extract orbits.

By repeating the procedure explained above for all 23 chromosomes, we
will have graphlets for all contact maps.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
        \PY{k+kn}{import} \PY{n+nn}{cv2}
        \PY{k+kn}{from} \PY{n+nn}{utility} \PY{k+kn}{import} \PY{o}{*}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n}{normalization}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
        \PY{k+kn}{import} \PY{n+nn}{os}
        \PY{o}{\PYZpc{}}\PY{k}{load\PYZus{}ext} autoreload
        \PY{o}{\PYZpc{}}\PY{k}{autoreload} 2
        \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
\end{Verbatim}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['all', 'colors', 'log']
`\%matplotlib` prevents importing * from pylab and numpy
  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"

@@

    \subsection{Initiating matrices}\label{initiating-matrices}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}18}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{2}
         \PY{n}{chr2} \PY{o}{=} \PY{n}{chr1}
         \PY{k}{print} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{chromosome 1: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{, chromosome 2: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
         \PY{c+c1}{\PYZsh{}print observed\PYZus{}mit\PYZus{}original.shape}

         \PY{n}{mit} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}MIT/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
                       \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
         \PY{n}{call4} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}call4/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
                         \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
         \PY{n}{rl} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}RL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

         \PY{n+nb}{all} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}ALL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

         \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
         \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
         \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
         \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
         \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
         \PY{n}{blankRows} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
         \PY{n}{blankCols} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows0}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows1}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows2}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows3}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols0}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols1}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols2}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
         \PY{n}{mit} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n+nb}{all} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n}{rl} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n}{call4} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
chromosome 1: 2, chromosome 2: 2
file directory: ../data/extracted\_all\_contact\_MIT/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_call4/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_RL/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_ALL/chr\_02\_02\_500kb.mat
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}19}]:} \PY{n}{n0}\PY{p}{,} \PY{n}{m0} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
         \PY{n}{n3}\PY{p}{,} \PY{n}{m3} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}

         \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n0}\PY{p}{,} \PY{n}{m0}\PY{p}{,} \PY{n}{n1}\PY{p}{,} \PY{n}{m1}\PY{p}{,} \PY{n}{n2}\PY{p}{,} \PY{n}{m2}\PY{p}{,} \PY{n}{n3}\PY{p}{,} \PY{n}{m3}\PY{p}{]}\PY{p}{)}

         \PY{n}{images} \PY{o}{=} \PY{p}{[}\PY{n}{mit}\PY{p}{,} \PY{n+nb}{all}\PY{p}{,} \PY{n}{rl}\PY{p}{,} \PY{n}{call4}\PY{p}{]}
         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
\end{Verbatim}

@@

    \begin{verbatim}
<matplotlib.figure.Figure at 0x7f65c3721610>
    \end{verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_4_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}20}]:} \PY{n}{mit} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{mit}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)} 
         \PY{n+nb}{all} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{rl} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{rl}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)} 
         \PY{n}{call4} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{call4}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)} 
\end{Verbatim}

>>>>

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{02\_graphlet\_correlation\_Analysis}

@@

    \section{Graphlet Correlation
Analysis}\label{graphlet-correlation-analysis}

Remember, in notebook \emph{Thresholding}, I thresholded contact maps
and saved so that orca can read them.

In this notebook, I perform two actions: 1. I apply \texttt{count5}
procedure in orca to extract 73 orbits for each loci in each chromosome.
After this stage, graphlets will be save with \texttt{.graphlets}
extension in the \texttt{./data} folder.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  I then read the graphlets and find both loci-wise distance and
  graphlet-wise correlations between the four cell lines.
\end{enumerate}

By repeating steps 1 and 2 for all 23 chromosomes, I will have pairwise
MIC values for all orbits of all cell lines. I would eventually be able
to have a data array of shape \texttt{A(23\ *\ 73)}, for each pair of
cell lines where \texttt{A{[}i,\ j{]}} denotes the correlation between
the jth orbit in the ith chromosome.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}102}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
          \PY{k+kn}{import} \PY{n+nn}{cv2}
          \PY{k+kn}{from} \PY{n+nn}{utility} \PY{k+kn}{import} \PY{o}{*}
          \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
          \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n}{normalization}
          \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
          \PY{k+kn}{import} \PY{n+nn}{os}
          \PY{o}{\PYZpc{}}\PY{k}{load\PYZus{}ext} autoreload
          \PY{o}{\PYZpc{}}\PY{k}{autoreload} 2
          \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
\end{Verbatim}

@@

    \section{1. Orbit Extraction:}\label{orbit-extraction}

The following R-script reads edge files (\texttt{.edges}) corresponding
to a chromosome under \texttt{data/} directory. It then writes the
resulting orbits into \texttt{data/*.graphlets}.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}2}]:} \PY{c+c1}{\PYZsh{}for chr1 in range(1, 24):}
        \PY{c+c1}{\PYZsh{}    os.system(\PYZsq{}Rscript rscript.r \PYZpc{}s\PYZsq{}\PYZpc{}chr1)}
\end{Verbatim}

    \section{2. Loci-wise Distance:}\label{loci-wise-distance}

I can now read the orbitfiles and put them into a \(N \times O\) matrix
where \(N\) denotes number of loci in the chromosome and \(O\) denotes
the number or obitals extracted, which can be either 14 or 73 (depending
on whether \texttt{count4()} or \texttt{count5()} are called in the
R-script above.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}152}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{2}
          \PY{n}{graphlets\PYZus{}mit} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}mit.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
          \PY{n}{graphlets\PYZus{}all} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}all.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
          \PY{n}{graphlets\PYZus{}rl} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}rl.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
          \PY{n}{graphlets\PYZus{}call4} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}call4.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
          \PY{k}{print}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
          \PY{k}{print}\PY{p}{(}\PY{n}{graphlets\PYZus{}all}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
          \PY{k}{print}\PY{p}{(}\PY{n}{graphlets\PYZus{}rl}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
          \PY{k}{print}\PY{p}{(}\PY{n}{graphlets\PYZus{}call4}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
file directory: data/chr02\_chr02\_mit.graphlets
file directory: data/chr02\_chr02\_all.graphlets
file directory: data/chr02\_chr02\_rl.graphlets
file directory: data/chr02\_chr02\_call4.graphlets
(478, 73)
(478, 73)
(478, 73)
(478, 73)

@@

    Calculating Loci-wise correlations:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}153}]:} \PY{n}{mit\PYZus{}all\PYZus{}corr} \PY{o}{=} \PYZbs{}
              \PY{n}{graphlet\PYZus{}correlational\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{p}{,} \PY{n}{graphlets\PYZus{}all}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}154}]:} \PY{n}{mit\PYZus{}mit\PYZus{}corr} \PY{o}{=} \PYZbs{}
              \PY{n}{graphlet\PYZus{}correlational\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{p}{,} \PY{n}{graphlets\PYZus{}mit}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}155}]:} \PY{n}{mit\PYZus{}call4\PYZus{}corr} \PY{o}{=} \PYZbs{}
              \PY{n}{graphlet\PYZus{}correlational\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{p}{,} \PY{n}{graphlets\PYZus{}call4}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}156}]:} \PY{n}{mit\PYZus{}rl\PYZus{}corr} \PY{o}{=} \PYZbs{}
              \PY{n}{graphlet\PYZus{}correlational\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{p}{,} \PY{n}{graphlets\PYZus{}rl}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}157}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
          \PY{n}{images} \PY{o}{=} \PY{p}{[} \PY{n}{mit\PYZus{}mit\PYZus{}corr}
                    \PY{p}{,} \PY{n}{mit\PYZus{}all\PYZus{}corr}
                   \PY{p}{,} \PY{n}{mit\PYZus{}rl\PYZus{}corr}
                   \PY{p}{,} \PY{n}{mit\PYZus{}call4\PYZus{}corr}\PY{p}{]}
          \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
\end{Verbatim}

@@

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_11_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}161}]:} \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Total correlation statistics}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit\PYZus{}mit\PYZus{}corr}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs mit}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit\PYZus{}all\PYZus{}corr}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs all}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit\PYZus{}rl\PYZus{}corr}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs rl}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit\PYZus{}call4\PYZus{}corr}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs call4}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

          \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s2}{Total correlation statistics}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}mit\PYZus{}corr}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs mit}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}all\PYZus{}corr}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs all}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}rl\PYZus{}corr}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs rl}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}call4\PYZus{}corr}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs call4}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Total correlation statistics
\#-----------------------------------------------------------------------\#
Stats for mit vs mit: 
max: 4.469689 | min: 0.000000 | median: 0.118804 | mean: 0.177694 | std: 0.406987
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for mit vs all: 
max: 4.469821 | min: 0.000000 | median: 0.254837 | mean: 0.331607 | std: 0.424543
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for mit vs rl: 
max: 4.469689 | min: 0.000000 | median: 0.368116 | mean: 0.429916 | std: 0.418677
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for mit vs call4: 
max: 4.469790 | min: 0.000000 | median: 0.296439 | mean: 0.359209 | std: 0.420711
\#-----------------------------------------------------------------------\#

Total correlation statistics
\#-----------------------------------------------------------------------\#
Stats for mit vs mit: 
max: 0.000000 | min: 0.000000 | median: 0.000000 | mean: 0.000000 | std: 0.000000
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for mit vs all: 
max: 1.805932 | min: 0.000000 | median: 0.243699 | mean: 0.287908 | std: 0.178464
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for mit vs rl: 
max: 1.235199 | min: 0.000000 | median: 0.368138 | mean: 0.391644 | std: 0.196214
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for mit vs call4: 
max: 1.392509 | min: 0.000000 | median: 0.298928 | mean: 0.317962 | std: 0.175240
\#-----------------------------------------------------------------------\#
